\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-12-01 papers/jss/article.Rnw
Use shorter ocpu URL
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@920 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{verbatim}
  GET https://public.opencpu.org/ocpu/library/MASS/data/Animals/pb
\end{verbatim}
The postfix \code{/pb} in the URL tells the server to send this
object in the form of a Protocol Buffer message.
% Alternative formats include \code{/json}, \code{/csv}, \code{/rds} and others.
If the request
is successful, OpenCPU returns the serialized object with HTTP status
code 200 and HTTP response header \code{Content-Type: application/x-protobuf}.
The latter is the conventional MIME type that formally notifies the client to
interpret the response as a Protocol Buffer.

@@

req <- GET('https://public.opencpu.org/ocpu/library/MASS/data/Animals/pb')
output <- unserialize_pb(req$content)

@@

req = urllib2.Request('https://public.opencpu.org/ocpu/library/MASS/data/Animals/pb')
res = urllib2.urlopen(req)

@@

req <- POST (
  url = "https://public.opencpu.org/ocpu/library/stats/R/rnorm/pb",
  body = payload,
  add_headers (
    "Content-Type" = "application/x-protobuf"
  )
)

>>>>

\begin{verbatim}
  GET https://demo.ocpu.io/MASS/data/Animals/pb
\end{verbatim}
The postfix \code{/pb} in the URL tells the server to send this
object in the form of a Protocol Buffer message.
% Alternative formats include \code{/json}, \code{/csv}, \code{/rds} and others.
If the request
is successful, OpenCPU returns the serialized object with HTTP status
code 200 and HTTP response header \code{Content-Type: application/x-protobuf}.
The latter is the conventional MIME type that formally notifies the client to
interpret the response as a Protocol Buffer.

@@

req <- GET('https://demo.ocpu.io/MASS/data/Animals/pb')
output <- unserialize_pb(req$content)

@@

req = urllib2.Request('https://demo.ocpu.io/MASS/data/Animals/pb')
res = urllib2.urlopen(req)

@@

req <- POST (
  url = "https://demo.ocpu.io/stats/R/rnorm/pb",
  body = payload,
  add_headers (
    "Content-Type" = "application/x-protobuf"
  )
)
